Grappa: Scalable Computing on Mass-Market Hardware for Irregular, Low-Locality Applications

### 2012-07-22 doc/asplos13/grappa.tex
Small changes.

In this section we describe the Grappa runtime system
(Figure~\ref{fig:grappa}). Grappa provides three key capabilities. The
first is a distributed shared \textbf{global memory} with high aggregate
random access bandwidth. The second is a \textbf{tasking} system with
lightweight multithreading and automatic load balancing through work
stealing. Finally, under the hood, a \textbf{communication} layer uses
network packet scheduling and aggregation to achieve high performance
while remaining largely invisible to applications. We now discuss the
programmer's view of Grappa's main capabilities, including a subset of
the Grappa API. In Section~\ref{implementation}, we discuss the details
of their implementation.

>>>>

The Grappa runtime system (Figure~\ref{fig:grappa}) supports scaling of irregular applications via three key components:
a \textbf{distributed shared global memory} providing high aggregate random access bandwidth for both normal and synchronized operations;  
a \textbf{tasking system} with lightweight multithreading to tolerate latency and workstealing to automate load balance;
and a \textbf{communication layer} using network packet scheduling and aggregation to achieve high performance while remaining largely invisible to applications.
Unlike many runtime systems where the task scheduler, memory access manager, and the communication  are separable subsystems, in Grappa these three components are tightly integrated and the performance of each depends heavily on that of the other two.  For example, eficiency of the communication layer requires that the tasking system multiplex tasks -- and the memory manager fetch data -- sufficiently rapidly to aggregate hundreds of individual requests into each packet; otherwise, the network will be poorly utilized.  Nonetheless, for simplicity of exposition, we describe each component in turn.

We now discuss the
programmer's view of Grappa's main capabilities, including a subset of
the Grappa API. In Section~\ref{implementation}, we discuss the details
of their implementation.
